FraCaS: 80 percent complete

### 2019-02-26 paper2018/paper.tex
more compression

\paragraph{Adverbs}
Another point, of minor theoretical importance but major practical
one, is our handling of adverbial phrases. We interpret adverbs (and
in general all adverbial and prepositional phrases) as VP-modifiers:
$Adv = VP → VP$, where $VP = object → Prop$. However, applying adverbs
to verb-phrases heavily complicates the Coq proofs, because such
phrases can contain quantifiers. Therefore, we instead move the
adverbs, so that they apply to (atomic) verbs only. Proofs can then be
simplify accordingly. \todo{theoretical justification in the
  literature?}

@@

FraCaS intends to classify each problem as either entailment (YES),
entailment of the opposite (NO) or no entailment (UNK).  In this work,
we have amended the FraCaS suite to correct a few problems. First,
certain test case are not formed correctly. Those were already
identified by Bill MacCartney\todo{cite} as such (using an ``undef''
labelling), and we removed those. Second, a few test cases occur twice
in the suite, but with two different labelling (one YES and one UNK),
with an annotation that those labellings correspond to different
readings. However, elsewhere in the suite, if a problem has several
readings but only one has entailment, it occurs only once and is
marked as YES. To make the test suite consistent, if one reading
yields entailment we have always considered it as YES. We have also
removed case 199 (which appears to be vacuous). Finally we changed the
labelling of the cases listed in Table \ref{tab:overrulings}, which appeared to have been
misclassified. We note that the majority of the mistaken
classifications occur in sections 3 and 4, which have not been
previously attempted and thus, we propose, have not been properly
scrutinized.
\begin{table}
  \centering
  \small
\begin{tabularx}{\columnwidth}{ccp{3.8cm}}
 test case & new class & comment \\ \hline
    005 & UNK & missing hypothesis: there are italian tenors \\
   056 &  Yes & Already identified as such by MacCartney \\
  069 & Unk & Mary could have used someone else's workstation \\
  119 & Unk & \textit{ibid.} \\
  181 & Yes & for the same reason as 180 \\
  226 & Yes &
\end{tabularx}
  \caption{Overruled FraCaS cases}
  \label{tab:overrulings}
\end{table}

@@

\paragraph{error analysis}
Our system fails to classify correctly 28 cases out of 259.  We give
here a summary of the missing features which are responsible for the
biggest number of failures. The one biggest source of error is an
incomplete handling of group readings. (FraCaS
013, 014, 046, 084, 111, 124, 126, 127, 137, 171, 172, 191, 193, 195, 243, 250, 333, 346). These
are cases where a syntactic conjunction of individuals is treated as a
semantic group, or where precise counting of the members of a group is
necessary.  Other problematic cases are where a definite plural does
not have a universal reading (091, 094, 095) --- these require an
analysis at the pragmatic level, which our system lacks. Additionally,
neither measure phrases (242) nor attributive comparatives (244, 245)
are handled.

>>>>

% \paragraph{Adverbs}
% Another point, of minor theoretical importance but major practical
% one, is our handling of adverbial phrases. We interpret adverbs (and
% in general all adverbial and prepositional phrases) as VP-modifiers:
% $Adv = VP → VP$, where $VP = object → Prop$. However, applying adverbs
% to verb-phrases heavily complicates the Coq proofs, because such
% phrases can contain quantifiers. Therefore, we instead move the
% adverbs, so that they apply to (atomic) verbs only. Proofs can then be
% simplify accordingly. \todo{theoretical justification in the
%   literature?}

@@

FraCaS intends to classify each problem as either entailment (YES),
entailment of the opposite (NO) or no entailment (UNK).  In this work,
we have amended the FraCaS suite to correct a few problems. First,
certain test case are not formed correctly. Those were already
identified by Bill MacCartney\todo{cite} as such (using an ``undef''
labelling), and we removed those. Second, a few test cases occur twice
in the suite, but with two different labelling (one YES and one UNK),
with an annotation that those labellings correspond to different
readings. However, elsewhere in the suite, if a problem has several
readings but only one has entailment, it occurs only once and is
marked as YES. To make the test suite consistent, if one reading
yields entailment we have always considered it as YES. We have also
removed case 199 (which appears to be vacuous). Finally we changed the
labelling of 6 cases 
% the cases listed in Table \ref{tab:overrulings},
which appeared to have been
misclassified (as justified in supplementary material). We note that the majority of the mistaken
classifications occur in sections 3 and 4, which have not been
previously attempted and thus, we propose, have not been properly
scrutinized.
% \begin{table}
%   \centering
%   \small
% \begin{tabularx}{\columnwidth}{ccp{3.8cm}}
%  test case & new class & comment \\ \hline
%     005 & UNK & missing hypothesis: there are italian tenors \\
%    056 &  Yes & Already identified as such by MacCartney \\
%   069 & Unk & Mary could have used someone else's workstation \\
%   119 & Unk & \textit{ibid.} \\
%   181 & Yes & for the same reason as 180 \\
%   226 & Yes &
% \end{tabularx}
%   \caption{Overruled FraCaS cases}
%   \label{tab:overrulings}
% \end{table}

@@

% \paragraph{error analysis}
% Our system fails to classify correctly 28 cases out of 259.  We give
% here a summary of the missing features which are responsible for the
% biggest number of failures. The one biggest source of error is an
% incomplete handling of group readings. (FraCaS
% 013, 014, 046, 084, 111, 124, 126, 127, 137, 171, 172, 191, 193, 195, 243, 250, 333, 346). These
% are cases where a syntactic conjunction of individuals is treated as a
% semantic group, or where precise counting of the members of a group is
% necessary.  Other problematic cases are where a definite plural does
% not have a universal reading (091, 094, 095) --- these require an
% analysis at the pragmatic level, which our system lacks. Additionally,
% neither measure phrases (242) nor attributive comparatives (244, 245)
% are handled.
